\begin{aquote}{Steven Moffat}
``People assume that time is a strict progression of cause to effect,
but {\em actually}, from a non-linear, non-subjective viewpoint--it's more like a
big ball of wibbly wobbly... time-y wimey... stuff.''
\end{aquote}

% Assuming SIGCOMM, not SOSP (less emphasis on general dst'sys)
Today's software-defined networking control platforms are highly complex,
distributing state between replicated
servers~\cite{floodlight},
providing isolation and resource arbitration between multiple
tenants~\cite{Casado:2010:VNF:1921151.1921162}, or
globally optimizing network utilization~\cite{urs}.
Most of this complexity comes from
fundamentally difficult distributed systems challenges that the networking community has
relatively little experience
solving in tightly coupled environments. % (not fully distributed)
For example, as Google's Urs H$\ddot{\mathrm{o}}$elzle recently
noted at the Open Networking Summit~\cite{urs}: ``[Coordination between replicated controllers] is going to
cause some angst, and justifiably, in the industry''. As SDN control software
is used to manage larger and more sophisticated networks,
we expect its complexity to increase.

With complexity inevitably come
bugs, and bug diagnosis is expensive and time consuming. A 2006 survey found
that developers at Microsoft spend 49\% of their
time troubleshooting bugs~\cite{msoft_concurrency}. The same study found that 70\% of the reported concurrency bugs
take days to months to fix, and almost 75\% of
respondents considered reproducibility to be hard or very hard.
To make matters worse, the number of hardware failures,
policy changes, host migrations, and other inputs to SDN controllers can
be quite large in production environments. Microsoft Research,
for example, reports 8.5 network error events per minute per
datacenter~\cite{Greenberg:2009:VSF:1592568.1592576}.
Consequently, it is often difficult to distinguish events that are
characteristic of normal operating
conditions from those that push the network into an erroneous state.
Despite the prevalence of failures, maintaining uptime is of critical importance; according to one
survey, ``meeting customer expectations about reliability'' is the second highest
priority for networking professionals~\cite{market_report}.
\scott{More SDN war stories, anecdotes
from Nicira, Big Switch}

% Software bugs cost $59 billion in 2002: bit.ly/V2Z7Al

A substantial part of the troubleshooting process today involves manually
identifying fault-inducing inputs
from logs of system executions where invalid configurations
were discovered. When asked to describe their
ideal tool, most admins said ``automated troubleshooting''~\cite{Zeng:Survey}.

In this paper we take a step towards realizing automated troubleshooting.
% thereby freeing developers to debug the problematic code itself.
We present an algorithm, \simulator, for automatically pruning extraneous
inputs from logs. What remains is a sequence of inputs that are both necessary and sufficient for
triggering a given bug.

Pruning only concurrent inputs (those that do not have a
happens-before chain~\cite{Lamport:1978:TCO:359545.359563} leading to the correctness violation)
does not yield a significant reduction in the log size. Our approach is
to apply the delta debugging algorithm~\cite{Zeller:2002:SIF:506201.506206}:
selectively prune events in the past and check at the end of
the modified execution whether the correctness violation remains.

Unlike the original intended use of delta debugging (minimizing a single
input file for a non-distributed program), the inputs in SDN logs are spread across
time and involve multiple machines. Adapting delta debugging to a distributed
setting requires much care when replaying modified inputs;
na\"ively replaying by simply maintaining relative timing between inputs often
fails to trigger the original correctness
violation. Input scheduling
needs to take internal events (\eg~mastership changes) into account to
preserve happens-before constraints. Yet by pruning inputs, the internal events
subtly change (consider the sequence numbers of packets),
and some internal events that occurred in the original
run may not occur after pruning prior inputs.
Our primary contribution is the insight that a small amount of domain knowledge
(codifcation of the syntax and semantics of events) can be applied to
place internal events into equivalence classes, allowing us to reason about the
differences between slightly altered histories.

Unlike previous work on troubleshooting dataplane behavior~\cite{handigol2012debugger}
and checking network invariants~\cite{hsa,anteater}, \simulator~is focused on troubleshooting
SDN control software.
%\Simulator~is complementary to proactive bug-finding techniques
%such as NICE~\cite{nice}, which work well for verifying crucial pieces of
%code but suffer from exponential
%state explosion when run on large systems.
\Simulator~is focused on erroneous
behavior of the overall distributed system (\eg~incorrect
failover logic), but is not specifically designed to troubleshoot bugs within a single controller
(\cf~deterministic replay~\cite{Dunlap:2002:REI:844128.844148}). The upshot of
this is our technique is not able to minimize all possible failures, such as
data races between threads. Nonetheless, the worst case for us is that the developer ends up with what they started:
an unpruned log.

Even the modest improvement of being able to minimize input
logs represents a
substantial improvement over the status quo;
to the best of our knowledge, painstaking analysis of detailed logs is the
current state-of-the-art in SDN platform troubleshooting.
% Main result from our work: the amount of effort it takes to codify domain knowledge is significantly less than the effort
% it would take to step through a normal replay debugger by hand for each bug.

% Cut?
The rest of this paper is organized as follows. In \S\ref{sec:overview},
we present an overview of the SDN stack and its failure modes.
In \S\ref{sec:approach} we present \simulator{} in detail.
We discuss use cases for \simulator{} in \S\ref{sec:architecture},
and explore case studies and a performance evaluation in
\S\ref{sec:evaluation}. We end by discussing the limitations of our
approach (\S\ref{sec:discussion}) and related work (\S\ref{sec:related_work}).

% ------------------------------------------------------------------- %
%    OLD OSDI TEXT:
\eat{

% Feedback from Ali Ghodsi:
%  - Why is S/W easier to test than H/W? It's not really this point that's
%    important either: it's the centralized control plane that makes it easier
%    to test. [rebuttal: cite Urs Hoelzle]
%  - SDN is not more challenging! (read: SDN doesn't not offer a challenge)
%    Not problematic that the difficulty hasn't chanfed -- just make it clear
%    that we aren't getting farther away from the distributed nature of
%    networks.
%  - Need to NAIL the motivation:
%      - Distributed systems are fundamentally hard to troubleshoot, and
%      they're going to remain that way forever.
%      - SDN provides an opportunity to do better than traceroute! In
%      traditional networks, configuration state is spread all over the place.
%      - Not trivial in SDN (aren't running away from distributed nature)
%        It presents a new challenge: how to verify high-level policies have
%        actually been implemented correctly? => enter correspondence checking.
%      - What's the key insight here?
%  - Say what W^3 stands for?
%  - Too much boiler plate
%  - How much do the readers learn from reading the introduction
%  - "It is important to place this work in context and scope the problem we are
%   attacking" is really lecturing the reader  ...  of course context and scope of
%   any research problem is important.

\colin{``Meeting Customer Expectations about Reliability'' is the second highest
priority for networking professionals, according to a market
report~\cite{market_report}}

Given their critical role in enterprises, one might expect that networks
would come with a well-developed suite of troubleshooting tools. However,
the unfortunate truth is that {\tt traceroute}, developed in 1987~\cite{traceroute},
remains the network administrator's most sophisticated diagnostic mechanism. This reflects
the lack of structure in network control planes, which are an ad hoc mixture of
distributed protocols and manual configuration that directly manipulate forwarding tables. It is hard to tell what is broken
when desired behavior is only implicitly expressed in the routing entries themselves, and that is the case with today's networks.

In this respect, the emergence of Software-Defined
Networks (SDN) provides both an opportunity and a challenge. Moving control logic out of hardware and into software
enables enables concise policy specifications and significantly more sophisticated testing and troubleshooting tools. Moreover, since SDN
is still in its infancy (compared to traditional networking approaches), we as a community have an opportunity to make diagnostic tools
a more integral part of the overall design process. Although SDN's goal is to simplify the
{\em management} of networks, the challenge is that the SDN software stack itself is a complex distributed system,
operating in asynchronous, heterogeneous, and failure-prone environments.
In this paper we present our approach to troubleshooting bugs in SDN control
software, a tool called \projectname{}.

\projectname{} simplifies the troubleshooting process by programmatically localizing the root cause
of network problems along three dimensions: {\it what} network problems exist at a
given point in time, {\it where} in the control software a problem first developed, and
{\it when} the triggering event occurred. To accomplish this
\projectname{} employs two techniques:

\noindent{\bf Correspondence Checking}. We observe that the structure of the
SDN software stack (as we discuss in the next section) enables a straightforward algorithm for
checking that control applications' policies are implemented correctly in
the physical network. Our algorithm enumerates all correctness violations
(\ie{}, any instance where the high-level policies are not properly
implemented by the SDN control software) present in the network at a given point in
time, providing a crisp determination of the range of inputs
and the system component(s) responsible for the fault.

\noindent{\bf \Simulator{}.} \projectname{} can replay the execution of the
system against
a stream of network events (e.g., link failures). This allows us to (i)
distinguish between correctness violations that are harmless and quickly heal and
those that are persistent, and (ii) identify the minimal set of events that triggered
the correctness violation.

% OSDI "Tips":
%  - Make very clear that we implemented it!
%  - Make very clear how this is an improvement over related work!
%  - What has the system's use showed about the practical implications of the
%    ideas?
%  - What have you learned from the work?
%  - How generally applicable are these ideas?
%  - What were the alternatives considered at various points?
%  - Keep forward references (to later sections) to a minimum

In combination, correspondence checking and \simulator{} programmatically
localize software-faults in the SDN software stack.
With \projectname{}, operators and developers are free to focus their efforts
on debugging the code itself, without needing to
diagnose the symptoms in the first place.
% This represents an improvement over the state-of-the-art SDN troubleshooting
% practices

It is important to place this work in context and scope the problem we are
attacking. First, \projectname{} is a troubleshooting tool, not a debugger; by
this we mean that \projectname{} helps identify and localize network
problems (what, where, and when?), but it does not help identify exactly which
line of code causes the error (why?). Second, \projectname{} is focused on the
system software of the SDN stack (described in the next section). While progress has been made in troubleshooting control
applications that run on top of the SDN platform~\cite{nice} and in troubleshooting the forwarding tables in the physical switches~\cite{anteater,hsa}, we
are not aware of previous troubleshooting work that focuses on the SDN
platform itself; to the best of our knowledge, painstaking analysis of detailed logs is the current state-of-the-art in SDN platform troubleshooting.

In evaluating \projectname{} on
three popular SDN platforms---Frenetic, Floodlight and POX---we found or reproduced several bugs:
isolation breaches and faulty failover logic between distributed controllers.
We also demonstrated the feasibility of deploying
\projectname{} on production networks,
finding that our tools can enumerate all correctness violations in
simulated networks exceeding 25,000 hosts in under 5 seconds.

The rest of this paper is organized as follows. In \S\ref{sec:overview},
we present an overview of the SDN stack and its failure modes.
In \S\ref{sec:approach} we present correspondence checking and
\simulator{} in detail. We discuss the design of \projectname{} in
\S\ref{sec:architecture}. In \S\ref{sec:evaluation} we present
three bugs found by \projectname{}, as well as a performance evaluation.
Finally, in \S\ref{sec:related_work} we discuss related work,
and in \S\ref{sec:conclusion} we conclude.

\colin{Reviewer OE seemed to think it was negative that we focus on
corner-case scenarios. We need to provide a stronger argument for why focus on
these}

\eat{
 % Feedback on version 2.0:
 % not clear what you mean by "SDN platform", "correctness violation"
\subsection{\colin{Feedback from Kay et al.}}
\begin{itemize}
\item Not sure that OSDI PC members will understand the subtleties of this statement: ``it is hard to tell what is broken when the goals are only implicitly expressed in the flow entries themselves.''
\item I think we should push a little harder on emphasizing that the bugs are really nasty, and fundamental to the distributed nature of the system. "may have bugs" seems a little weak.
\item We should make it very clear how our tools are an improvement over the status quo (log analysis). In particular, we automatically localize the (i) layer, and (ii) minimal causal set of events responsible for an error.
\item \simulator{} does two things: find the minimal causal set, {\bf and}
differentiates benign from pernicious. Only one of these points was clear, not
both.
\item The Google quote seems to indicate that the problem has already been solved!
\item Along a similar vein, the point about ``the SDN platform will eventually
become stable'' makes it seems like these problems aren't fundamental. But
these problems are fundamental! How will the community view this paper in 10
years?
\item The reader doesn't walk away from this problem thinking ``This problem
seems really heard!''. What are the specific bugs this framework addresses?
Also, make it clear why this problem is important! If Pepsi knows that
Coca-cola might be able to snoop on their traffic, we've lost huge \$\$\$.
\item Don't frame ourselves just against log analysis. Make
the shortcomings of the status quo very clear, and be very precise about how
we address those shortcoming. (Why aren't traditional distributed systems
techniques apropro? Why is static checking of a single layer insufficient? How
is \simulator{} different than traditional replay debugging?)
\item Would be cool to have numbers on how many log events developers have to
step through today.
\item Would also be cool to have numbers on how many benign correctness violations
there are at a given point (say, in POX).
\item ``Policy-violation'' wasn't well-defined.
\item The introduction (prose) was too dense. Frame the problem in terms that
the reader understands. Get them thinking about the problem right off the bat.
Then lead them through our reasoning of how we came to the solution. Present
a straw-man solution, and show why that doesn't work. This way
the reader is much more engaged -- the reader should ``nod along''.
\item What exactly are we simulating? Hardware faults? Misconfigurations?
(answer: all of the above)
\item How exactly does correspondence checking provide a crisp determination of the scope of a correctness violation in the
network as well as the range of inputs that produce it? (answer: you start off
with a customer complaint, ``A can't ping B''. Correspondence checking tells
you all possible inputs that would experience the blackhole, and what parts of
the network are effected)
\item ``Stack'' connotes TCP/IP. Maybe use ``Platform'' instead?
\item ``Fault'' connotes hardware failure. Maybe use ``Software Fault''
\item Cite Frenetic, POX, Floodlight?
\item What does \projectname{} stand for?
\end{itemize}
}

}
